article title

### 2022-07-23 pilon_gilles_glossary.tex
Fix error in independent plural
Update probable error description
Add Taguchi Loss Function

@@

    description={TBD}

@@

>>>>

    plural={independent variables}

@@

    description={Also called resolution. It is the interval within which a single measurement might occur 50 \% of the time, $\pm 0.6745 \times \sigma_\text{pure error}$}

@@

\newglossaryentry{taguchi_loss_function}
    name={Taguchi Loss Function},
    description={It is a graphical depiction of loss to describe a phenomenon affecting the value of products produced by a company. It was developed by the Japanese business statistician Genichi Taguchi.}
